SMT-Boosted Security Types for Low-Level MPC

### 2025-11-11 toplas26/metalang.tex
checkpoint

The use of pre and postconditions in \ttt{main} allows verification of
whole-program (protocol) correctness. Further, the use of annotations
on function definitions supports \emph{compositional} verification of
program components. In general postconditions can serve as
pre-verified properties of functions that can be reused in, and reduce
overhead of, whole protocol verification.

>>>>

The use of pre and postconditions in \ttt{main} allows verification of
whole-program (protocol) correctness. Further, the use of annotations
on function definitions supports \emph{compositional} verification of
program components. In general postconditions can serve as
pre-verified properties of functions that can be reused in, and reduce
overhead of, whole protocol verification. A representative example of
a GMW $\ttt{and}$ gate \cite{evans2018pragmatic} implementation is
given in Figure \ref{fig-gmwprepost}. Here, the $\ttt{andgmw}$
function takes as input strings $x$ and $y$ that distinguish values
secret-shared between clients 1 and 2 as $\mx{x}{1}, \mx{x}{2}$ and
$\mx{y}{1},\mx{y}{2}$ respectively-- that is, these shares encode
$\ttt{RECON}(x)$ and $\ttt{RECON}(y)$ The postcondition of the
protocol defined by the $\ttt{andgmw}$ specifies that it results in a
value shared between clients 1 and 2 as $\ttt{RECON}(z)$ that is the
conjunction of $\ttt{RECON}(x)$ and $\ttt{RECON}(y)$. This is
non-trivial to prove, and expressing this postcondition in a
compositional manner reduces proof overhead and improves scalability
to large circuits that may incorporate a multitude of $\ttt{and}$
gates.

\begin{fpfig}[t]{GMW $\ttt{and}$ gate with postcondition.}{fig-gmwprepost}
\begin{verbatimtab}
RECON(x) { (m[x]@1 + m[x]@2) }

andtablegmw(x, y, z) {
  let r11 = (r[z] + (m[x] + 1) * (m[y] + 1)) in
  let r10 = (r[z] + (m[x] + 1) * (m[y] + 0)) in
  let r01 = (r[z] + (m[x] + 0) * (m[y] + 1)) in
  let r00 = (r[z] + (m[x] + 0) * (m[y] + 0)) in
  { row1 = r11; row2 = r10; row3 = r01; row4 = r00 }
}

andgmw(z:string, x:string, y:string) {
  let table = andtablegmw(x,y,z) in
  m[z]@2 := OT4((m[x], m[y])@2, table.row4, table.row3, table.row2, table.row1)@1;
  m[z]@1 := r[z]@1
}
postcondition:  ( RECON(z) == RECON(x) * RECON(y))
\end{verbatimtab}
\end{fpfig}

### 2025-11-11 toplas26/metaty.tex
checkpoint

>>>>

\begin{fpfig}[t]{GMW $\ttt{and}$ gate with share type annotations.}{fig-gmwsharetypes}
\begin{verbatimtab}
andgmw(z:string, x:string, y:string) {
  let table = andtablegmw(x,y,z) in
  m[z]@2 := OT4((m[x], m[y])@2, table.row4, table.row3, table.row2, table.row1)@1;
  m[z]@1 := r[z]@1;
  m[z]@2 as (RECON(x) * RECON(y)) + r[z]@1;
  [m[z]@1,m[z]@2] : shares
}
postcondition:  ( RECON(z) == RECON(x) * RECON(y))
\end{verbatimtab}
\end{fpfig}
